---
title: "03-lab3"
format: html
editor: visual
---

## Quarto

Assignment question 1.

```{r}
library(knitr)

flye_assembly <- read_lines("outputs/flye_output/flye.log")

```

Based on the results we'd expect to ... and we'd say that the coverage was ...

Assignment question 2. 
- The BUSCO scores were 42.9% complete, 0.6% fragmented and 56.5% missing. The coverage given was not good as more than half the of genes were missing. - N50 was 28 Kbp.
- The total assembly length was 10055917 bp.

Assignment question 3. 
- The genome fraction compared to BUSCO was 4.733, which gave us a lesser percentage than the results in BUSCO. 
- Duplication ratio was 1.029 
- The level of misassemblies on the report was an output of 1 misassembled contig and the length was 18084. This tells us that the reference genome represents the genomic diversity really well for this species, as we only got a single misassembled contig.

Assignment question 4.

```{r}
samtools faidx data/S288C_UCSC.fna chrI > outputs/R64_chr1.fna
```

Assignment question 5. 
- We have 10 contigs aligned to chromosome 1. 
- By using range() and ranges() the length of chromosome 1 was 147212 and the sum of the contigs was 17070, so we'd estimate that 11.60% of the chromosome is covered by contigs.

Assignment question 6.

```{r}
sequences <- readDNAStringSet("outputs/medaka_round2/consensus.fasta")

longest_seq <- which.max(width(sequences))

longest_seq_true <- sequences[longest_seq]

writeXStringSet(longest_seq_true, filepath = "outputs/longest_contig.fasta")
```

Assignment question 7.

```{r}
samtools view -bS outputs/cds_aln.sam > outputs/cds_aln.bam
  
samtools sort outputs/cds_aln.bam -o outputs/cds_aln.sorted.bam

samtools index outputs/cds_aln.sorted.bam
```

Assignment question 8.

```{r}
bam_file <- "outputs/cds_aln.sorted.bam"

bam <- BamFile(bam_file)

alns <- readGAlignments(bam)

gr_alns <- granges(alns)

aln_track <- AnnotationTrack(gr_alns, name = "Contigs", genome = "sacCer3")

axis_track <- GenomeAxisTrack()

pdf("cds_aln_contigs.pdf", width = 10, height = 7)

plotTracks(list(axis_track, aln_track),
           from = min(start(gr_alns)),
           to = max(end(gr_alns)),
           main = "Contig Alignments to Chromosome 1")
dev.off()

```
